Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-30 src/article.tex

>>>>

% % Option 1
\begin{figure}
    \centering
    \includesvg[inkscapelatex=false, height = 0.4\textheight]{images/log_harp_outline}
    \caption{Logarithmic shape of an original Trasuntino harpsichord}
    \Description{}
    \label{fig:baffles}
\end{figure}

% % Option 2
\begin{figure}
    \centering
     \begin{subfigure}[h]{0.5\linewidth}
        \centering
        \includesvg[inkscapelatex=false, width = \linewidth]{images/log_harp_outline}            
        \caption{logarithmic shape}    
        \label{fig:log-harp}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.5\linewidth}
        \centering
        \includesvg[inkscapelatex=false, width = \linewidth]{images/49-key_outline}        
        \caption{replica shape}
        \label{fig:rect-harp}
    \end{subfigure}
    \caption{Logarithmic shape of an original Trasuntino harpsichord contrast with rectangular shape of the replica}    
    \Description{}
    \label{fig:baffles}
\end{figure}

% % Option 4

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Logarithmic shape of an original Trasuntino harpsichord}
    \Description{}
    \label{fig:baffles}
\end{figure}

% % Option 3
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{src/images/trasuntino-log-harp.jpg}    
    \caption{Logarithmic shape of an original Trasuntino harpsichord. Source: Image 3 Royal College of Music Collections Item RCM0002  \protect\footnote{\url{https://museumcollections.rcm.ac.uk/collection/Details/collect/58}}  } 
    \Description{}
    \label{fig:baffles}
\end{figure}
